Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints

### 2023-10-14 ms/ms.qmd
Bring in data to get some simple summary stats
Updated MS

@@

Here, we explore the first 1000 preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.

>>>>

```{r, setup}
#| label: setup

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl)

# Load in the data
  data <- read_xlsx(here("data", "20231003_EER_preprints_metadata.xlsx"))

pr <- length(unique(data$`Preprint ID`))
```

@@

Here, we explore the first preprints uploaded to *EcoEvoRxiv* to understand preprint practices and use in our field, focusing our attention on understanding: 1) how long it takes for a preprint to become published, and how many preprints remain unpublished; 2) what countries make use of preprints; 3) how career stage and gender impact preprint use; 4) whether data and code are more likely to be shared in preprints; and 5) the extent to which authors make use of preprint servers for registered reports and community driven peer review.

We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the 3rd October 2023).
